Hydra Battles and Cie

### 2021-08-31 doc/part-hydras.tex
use of inputsnippets in Chap3
correct a typo in part-hydras.tex

\inputsnippets{Omega_Small/mGeb, omega_Small/mGez,
  Omega_Small/omegaSmallz}

@@

\input{movies/snippets/ON_Omega2/Merge}

@@

 \input{movies/snippets/ON_Finite/t0Empty}

\begin{Coqsrc}
Program Definition bad : t 10 := 10.
Next Obligation.
\end{Coqsrc}

\begin{Coqanswer}
1 subgoal (ID 118)

  ============================
  10 <? 10 
\end{Coqanswer}

\begin{Coqsrc}
  compute.
Abort.
\end{Coqsrc}

%\input{movies/snippets/ON_Finite/bad}

@@

\begin{Coqanswer}
 1 subgoal (ID 110)

  n, x0 : nat
  i, i0 : x0 <? S n
  ============================
  exist (fun i1 : nat => i1 <=? n) x0 i =
  exist (fun i1 : nat => i1 <=? n) x0 i0
\end{Coqanswer}

@@

\begin{Coqanswer}
1 subgoal (ID 112)

  n, x0 : nat
  i, i0 : x0 <? S n
  ============================
  i = i0
\end{Coqanswer}

@@

@@

@@

@@

\input{movies/snippets/ON_Finite/InclIJ}
\input{movies/snippets/ON_Finite/InclIJa}
\input{movies/snippets/ON_Finite/InclIJb}
\input{movies/snippets/ON_Finite/InclIJc}
\input{movies/snippets/ON_Finite/InclIJd}

@@

%%% TODO : link to Comparable and StrictOrder classes

@@

% \vspace{4pt}
% \emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#compare_refl}{Epsilon0.T1}}

% \begin{Coqsrc}
% Lemma compare_refl : forall alpha, compare alpha alpha =  Eq.
% \end{Coqsrc}

% \begin{Coqsrc}
% Lemma compare_reflect : forall alpha beta,
%     match compare alpha beta with
%     |   Lt => lt alpha  beta
%     |   Eq => alpha = beta
%     |   Gt => lt beta  alpha
%     end.
% \end{Coqsrc}

% We prove also that the relation \texttt{lt} is a strict total order.

% \vspace{4pt}
% \emph{From Module~\href{../theories/html/hydras.Epsilon0.T1.html\#lt_irrefl}{Epsilon0.T1}}

% \begin{Coqsrc}
% Theorem lt_irrefl (alpha: T1):  ~ lt alpha alpha.

% Theorem lt_trans (alpha beta gamma : T1) :
%   lt alpha  beta -> lt beta gamma -> lt alpha gamma.

% Definition lt_eq_lt_dec  :
%    forall alpha beta : T1, 
%           {lt alpha  beta} + {alpha = beta} + {lt beta alpha}.
% \end{Coqsrc}

% \vspace{4pt}

% Please note that the order \texttt{lt} is not reflected 
% in the structure (size and/or height) of the terms of \texttt{T1}.

% \begin{Coqsrc}
% Example Ex0:
%   lt (ocons (phi0 (phi0 omega)) 2
%             (ocons (phi0 10) 33
%                    (ocons (phi0 9) 63 zero)))
%      (ocons  (phi0 (phi0 omega)) 2 (phi0 (phi0 11))).
% Proof.
%   reflexivity. 
% Qed.
% \end{Coqsrc}

% Uncomment for testing 
%\textbf{Todo: Fix subgoal display }
%\input{movies/snippets/T1/compareRev}

>>>>

\inputsnippets{Omega_Small/mGeb, Omega_Small/mGez,
  Omega_Small/omegaSmallz}

@@

\inputsnippets{ON_Omega2/Merge, ON_Omega2/Mergeb}

@@

 \inputsnippets{ON_Finite/t0Empty, ON_Finite/bad10}

\subsubsection{Comparison function}

@@

\input{movies/snippets/ON_Finite/compareCorrectb}

@@

\input{movies/snippets/ON_Finite/compareCorrectc}

@@

\inputsnippets{ON_Finite/compareCorrectd}

@@

\subsubsection{Building an instance of \texttt{ON}}

@@

\vspace{10pt}

@@

\vspace{10pt}

\noindent\emph{From Module~\href{../theories/html/hydras.OrdinalNotations.ON_Finite.html}{OrdinalNotations.ON\_Finite}}

\inputsnippets{ON_Finite/InclIJ, ON_Finite/InclIJa,
  ON_Finite/InclIJb,ON_Finite/InclIJc, ON_Finite/InclIJd,
ON_Finite/InclIJz}

@@

@@
